### 2016-06-21 docs/ms_communitySynchrony.Rmd
adds correlation of cv and pgr synch to ms

table_data <- alltable_data[,c("Site", "V1", "V4", "V7")]
table_data$spp <- c(length(unique(az_data$species)),
                    length(unique(id_data$species)),
                    length(unique(ks_data$species)),
                    length(unique(mt_data$species)),
                    length(unique(nm_data$species)))
colnames(table_data) <- c("Site",
                          "$\\phi_{R}$", 
                          "$\\phi_{C}$",
                          "CV of Total Cover",
                          "Species richness")
myorder <- c(5,1,3,4,2)
xtable_data <- table_data[myorder,]
# colnames(table_data) <- c("Site",
#                           "$\\phi_{r}$", 
#                           "$\\text{E}(\\phi_{r})$", 
#                           "$\\text{E}(\\sigma_{r,c} + \\sigma_{r,e})$",
#                           "$\\phi_{C}$", 
#                           "$\\text{E}(\\phi_{C})$",
#                           "$\\text{E}(\\sigma_{C,c} + \\sigma_{C,e})$",
#                           "CV of Total Cover",
#                           "Species richness")
# table_data[,3] <- round(1/table_data[,ncol(table_data)],2) # reset expected sybchrony to 1/S
# table_data[,4] <- table_data[,2] - table_data[,3] # calculate obs - exp synchrony

>>>>

table_data <- alltable_data[,c("Site", "V1", "V4", "V7")]
table_data$spp <- c(length(unique(az_data$species)),
                    length(unique(id_data$species)),
                    length(unique(ks_data$species)),
                    length(unique(mt_data$species)),
                    length(unique(nm_data$species)))
colnames(table_data) <- c("Site",
                          "$\\phi_{R}$", 
                          "$\\phi_{C}$",
                          "CV of Total Cover",
                          "Species richness")
myorder <- c(5,1,3,4,2)
xtable_data <- table_data[myorder,]
sink(file = "../results/correlation_Rsynch_cv.txt")
cat("correlation between synchrony of growth rates and cover CV is:")
cor(table_data$`CV of Total Cover`, table_data[,2])
Sys.Date()
sink()
# colnames(table_data) <- c("Site",
#                           "$\\phi_{r}$", 
#                           "$\\text{E}(\\phi_{r})$", 
#                           "$\\text{E}(\\sigma_{r,c} + \\sigma_{r,e})$",
#                           "$\\phi_{C}$", 
#                           "$\\text{E}(\\phi_{C})$",
#                           "$\\text{E}(\\sigma_{C,c} + \\sigma_{C,e})$",
#                           "CV of Total Cover",
#                           "Species richness")
# table_data[,3] <- round(1/table_data[,ncol(table_data)],2) # reset expected sybchrony to 1/S
# table_data[,4] <- table_data[,2] - table_data[,3] # calculate obs - exp synchrony
